Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-11 paper/paper.tex
Change Glasgow description a bit

\paragraph{Algorithms selected in our portfolio.}
We have selected a set of algorithms with complementary performance:
\begin{itemize}
\item VF2 \cite{Cordella:2004}, which performs a weak filtering so that it is especially fast on trivially satisfiable instances;
\item LAD \cite{Solnon:2010}, which combines two strong but expensive filtering techniques (AllDifferent Generalized Arc Consistency and LAD);
\item Glasgow \cite{McCreesh:2015}, which does an expensive preprocessing based on path length invariant properties, followed by weaker filtering (forward-checking) during search. We consider 4 different instanciations of Glasgow, with path lengths varying from 1 to 4: The longer the path, the stronger the reduction, and the more expensive to achieve.
\end{itemize}

The Glasgow algorithm has a parameter, which controls the lengths of paths used
when reasoning about non-adjacent vertices.  In experiments reported in
\cite{McCreesh:2015}, the choice of paths of length 3 was used as a reasonable
compromise -- longer paths lead to prohibitively expensive preprocessing on
larger, denser instances. This is often not the best choice on an instance by
instance basis: sometimes path-based reasoning gives no benefit at all,
sometimes considering only paths of length 2 suffices, occasionally paths of
length 4 are helpful, and even looking at paths of length 3 is relatively
expensive on some graphs.

@@

Figure~\ref{fig:ecdf-glasgow} shows the cumulative distribution function for the
Glasgow algorithm with four different path lengths. As the instances become
harder to solve, longer paths become better. This is what we expect, as more
reasoning is expensive, but potentially increases the reduction of the search
space. In particular, the relative performance of the algorithms is monotone in
the time it takes to solve the instance -- path length 1 is best at first, but
gets worse as the time to solve the instance increases until path length 2 is
better. After that point, length 1 is never better than length 2 again. The same
is true for the other path lengths.

>>>>

\paragraph{Algorithms selected in our portfolio.}
We have selected a set of algorithms with complementary performance:
\begin{itemize}
\item VF2 \cite{Cordella:2004}, which performs a weak filtering so that it is especially fast on trivially satisfiable instances;
\item LAD \cite{Solnon:2010}, which combines two strong but expensive filtering techniques (AllDifferent Generalized Arc Consistency and LAD);
\item Glasgow \cite{McCreesh:2015}, which does expensive preprocessing based on path length
    invariant properties to generate additional constraints, followed by weaker filtering
    (forward-checking, and a heuristic AllDifferent propagator which can miss deletions) and
    conflict-directed backjumping during search.
\end{itemize}

\noindent The Glasgow algorithm has a parameter, which controls the lengths of paths used when
reasoning about non-adjacent vertices.  In experiments reported in \cite{McCreesh:2015}, the choice
of paths of length 3 was used as a reasonable compromise---longer paths lead to prohibitively
expensive preprocessing on larger, denser instances. This is often not the best choice on an
instance by instance basis: sometimes path-based reasoning gives no benefit at all, sometimes
considering only paths of length 2 suffices, occasionally paths of length 4 are helpful, and even
looking at paths of length 3 is relatively expensive on some graphs.

@@

Figure~\ref{fig:ecdf-glasgow} shows the cumulative distribution function for the
Glasgow algorithm with four different path lengths. As the instances become
harder to solve, longer paths become better. This is what we expect, as more
reasoning is expensive, but potentially increases the reduction of the search
space. In particular, the relative performance of the algorithms is monotone in
the time it takes to solve the instance---path length 1 is best at first, but
gets worse as the time to solve the instance increases until path length 2 is
better. After that point, length 1 is never better than length 2 again. The same
is true for the other path lengths.
